# Filename: print-stmt-quantile-analysis.Rmd

# About: 
 - This R script reads the whole CSV file containing all the projects with their scores. 
 - The script then firstly cleans the data, then seperates the data based on project 1, 2, 3, or 4, then further seperates the data based on the score of the project. 
 - The final separation is done by calculating quantiles of each of the project scores and then listing the projects into groups for each quantiles.


# Read the CSV file containing all the project scores
```{r echo=TRUE}
library(data.table)
library(dplyr)
library(bit64)

project_scores <- fread("/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/web-cat-all_output_submission_data.csv")

```

# Cleaning the data

```{r echo=TRUE}
project_scores <- na.omit(project_scores)
```

# Create data.table for each of the 4 projects

```{r echo=TRUE}
project_1_scores <- filter(project_scores, project_scores$assignment == 'Project 1')
project_2_scores <- filter(project_scores, project_scores$assignment == 'Project 2')
project_3_scores <- filter(project_scores, project_scores$assignment == 'Project 3')
project_4_scores <- filter(project_scores, project_scores$assignment == 'Project 4')
```

# Generating Quantiles for each of the 4 projects

```{r echo-TRUE}
quantile(project_1_scores$score.correctness)
quantile(project_2_scores$score.correctness)
quantile(project_3_scores$score.correctness)
quantile(project_4_scores$score.correctness)

#Overall
quantile(project_scores$score.correctness)
```

# Storing quantial values

``` {r echo=TRUE}

# Project 1 quantiles

proj_1_quantile <- c(quantile(project_1_scores$score.correctness)[[1]], quantile(project_1_scores$score.correctness)[[2]],
quantile(project_1_scores$score.correctness)[[3]],
quantile(project_1_scores$score.correctness)[[4]],
quantile(project_1_scores$score.correctness)[[5]])


# Project 2 quantiles

proj_2_quantile <- c(quantile(project_2_scores$score.correctness)[[1]], quantile(project_2_scores$score.correctness)[[2]],
quantile(project_2_scores$score.correctness)[[3]],
quantile(project_2_scores$score.correctness)[[4]],
quantile(project_2_scores$score.correctness)[[5]])


# Project 1 quantiles

proj_3_quantile <- c(quantile(project_3_scores$score.correctness)[[1]], quantile(project_3_scores$score.correctness)[[2]],
quantile(project_3_scores$score.correctness)[[3]],
quantile(project_3_scores$score.correctness)[[4]],
quantile(project_3_scores$score.correctness)[[5]])


# Project 1 quantiles

proj_4_quantile <- c(quantile(project_4_scores$score.correctness)[[1]], quantile(project_4_scores$score.correctness)[[2]],
quantile(project_4_scores$score.correctness)[[3]],
quantile(project_4_scores$score.correctness)[[4]],
quantile(project_4_scores$score.correctness)[[5]])

```

# Seperating student projects based on the score quantiles 
```{r echo=TRUE}

# Project 1

temp_proj <- project_1_scores
temp_quantile <- proj_1_quantile

proj_1_q_0_to_25_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[1] & temp_proj$score.correctness < temp_quantile[2] )

proj_1_q_25_to_50_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[2] & temp_proj$score.correctness < temp_quantile[3] )

proj_1_q_50_to_75_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[3] & temp_proj$score.correctness < temp_quantile[4] )

proj_1_q_75_to_100_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[4] & temp_proj$score.correctness <= temp_quantile[5] )

# Project 2

temp_proj <- project_2_scores
temp_quantile <- proj_2_quantile

proj_2_q_0_to_25_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[1] & temp_proj$score.correctness < temp_quantile[2] )

proj_2_q_25_to_50_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[2] & temp_proj$score.correctness < temp_quantile[3] )

proj_2_q_50_to_75_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[3] & temp_proj$score.correctness < temp_quantile[4] )

proj_2_q_75_to_100_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[4] & temp_proj$score.correctness <= temp_quantile[5] )

# Project 3

temp_proj <- project_3_scores
temp_quantile <- proj_3_quantile

proj_3_q_0_to_25_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[1] & temp_proj$score.correctness < temp_quantile[2] )

proj_3_q_25_to_50_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[2] & temp_proj$score.correctness < temp_quantile[3] )

proj_3_q_50_to_75_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[3] & temp_proj$score.correctness < temp_quantile[4] )

proj_3_q_75_to_100_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[4] & temp_proj$score.correctness <= temp_quantile[5] )


# Project 4

temp_proj <- project_4_scores
temp_quantile <- proj_4_quantile

proj_4_q_0_to_25_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[1] & temp_proj$score.correctness < temp_quantile[2] )

proj_4_q_25_to_50_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[2] & temp_proj$score.correctness < temp_quantile[3] )

proj_4_q_50_to_75_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[3] & temp_proj$score.correctness < temp_quantile[4] )

proj_4_q_75_to_100_list <- filter(temp_proj, temp_proj$score.correctness >= temp_quantile[4] & temp_proj$score.correctness <= temp_quantile[5] )

```

# Outputting scores for each of the 4 projects

```{r echo=TRUE}
write.csv(project_1_scores, "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/Projectwise_scores/project_1_scores.csv", row.names=FALSE)
write.csv(project_2_scores, "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/Projectwise_scores/project_2_scores.csv", row.names=FALSE)
write.csv(project_3_scores, "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/Projectwise_scores/project_3_scores.csv", row.names=FALSE)
write.csv(project_4_scores, "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/Projectwise_scores/project_4_scores.csv", row.names=FALSE)
```

# Outputting list of student project scores based on the quantile values

```{r echo=TRUE}

# Project 1

write.csv(proj_1_q_0_to_25_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 1/proj_1_q_0_to_25_list.csv"
          ,row.names = FALSE)
write.csv(proj_1_q_25_to_50_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 1/proj_1_q_25_to_50_list.csv"
          ,row.names = FALSE)
write.csv(proj_1_q_50_to_75_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 1/proj_1_q_50_to_75_list.csv"
          ,row.names = FALSE)
write.csv(proj_1_q_75_to_100_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 1/proj_1_q_75_to_100_list.csv"
          ,row.names = FALSE)

# Project 2

write.csv(proj_2_q_0_to_25_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 2/proj_2_q_0_to_25_list.csv"
          ,row.names = FALSE)
write.csv(proj_2_q_25_to_50_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 2/proj_2_q_25_to_50_list.csv"
          ,row.names = FALSE)
write.csv(proj_2_q_50_to_75_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 2/proj_2_q_50_to_75_list.csv"
          ,row.names = FALSE)
write.csv(proj_2_q_75_to_100_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 2/proj_2_q_75_to_100_list.csv"
          ,row.names = FALSE)

# Project 3

write.csv(proj_3_q_0_to_25_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 3/proj_3_q_0_to_25_list.csv"
          ,row.names = FALSE)
write.csv(proj_3_q_25_to_50_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 3/proj_3_q_25_to_50_list.csv"
          ,row.names = FALSE)
write.csv(proj_3_q_50_to_75_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 3/proj_3_q_50_to_75_list.csv"
          ,row.names = FALSE)
write.csv(proj_3_q_75_to_100_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 3/proj_3_q_75_to_100_list.csv"
          ,row.names = FALSE)

# Project 4

write.csv(proj_4_q_0_to_25_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 4/proj_4_q_0_to_25_list.csv"
          ,row.names = FALSE)
write.csv(proj_4_q_25_to_50_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 4/proj_4_q_25_to_50_list.csv"
          ,row.names = FALSE)
write.csv(proj_4_q_50_to_75_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 4/proj_4_q_50_to_75_list.csv"
          ,row.names = FALSE)
write.csv(proj_4_q_75_to_100_list,
          "/Dr. Cliff Shaffer's Lab/DPS Classify and Analysis Oct, 2018/Analysis by Quantile Values Nov 2018/QuantileScoreWise/Project 4/proj_4_q_75_to_100_list.csv"
          ,row.names = FALSE)

```